\begin{thebibliography}{99}

\bibitem[1]{kurose2017} 
    J. F. Kurose and K. W. Ross, \textit{Computer Networking: A Top-Down Approach}, 7th ed. Pearson, 2017.

\bibitem[2]{tanenbaum2010} 
    A. S. Tanenbaum and D. J. Wetherall, \textit{Computer Networks}, 5th ed. Pearson, 2010.

\bibitem[3]{gfg_network_devices} 
    GeeksforGeeks, ``Network Devices (Hub, Repeater, Bridge, Switch, Router, Gateways and Brouter),'' \textit{GeeksforGeeks}. [Trực tuyến]. Available: \url{https://www.geeksforgeeks.org/computer-networks/network-devices-hub-repeater-bridge-switch-router-gateways/}
\bibitem[4]{comer2018} 
    Douglas E. Comer, \textit{The Internet Book: Everything You Need to Know about Computer Networking and How the Internet Works}, CRC, 2018.

\bibitem[5]{ieee80211} 
    IEEE Computer Society, ``IEEE Standard for Information technology - Telecommunications and information exchange between systems Local and metropolitan area networks - Specific requirements - Part 11: Wireless LAN Medium Access Control (MAC) and Physical Layer (PHY) Specifications,'' \textit{IEEE Std 802.11-2020}, 2021.

\bibitem[6]{geeksforgeeks2023} 
    GeeksforGeeks, ``Difference between Infrastructure and Infrastructure-less Network,'' \textit{GeeksforGeeks}, 2023. [Online]. Available: \url{https://www.geeksforgeeks.org/difference-between-infrastructure-and-infrastructure-less-network/}

\bibitem[7]{ms_ibss_2021} 
    Microsoft Corporation, ``Native 802.11 Wireless LAN Architecture - Deprecation of IBSS,'' \textit{Microsoft Learn Documentation}, 2021. [Online]. Available: \url{https://learn.microsoft.com/en-us/windows-hardware/drivers/network/native-802-11-wireless-lan-architecture}
    
\end{thebibliography}